### 2016-07-02 2016_Proceedings_ISMIR/papers.tex
fixed compilation issues, switched to smaller times font for headers, footers, TOC, removed underscores from csv

\includepaper{TIME-DELAYED MELODY SURFACES FOR R_GA RECOGNITION}{Sankalp Gulati, Joan Serrà, Kaustuv Kanti Ganguli, Sertan _entürk and Xavier Serra}{articles/030_Paper}

@@

\includepaper{Further Steps towards a Standard Testbed for Optical Music Recognition}{Jan Haji_, jr., Ji_í Novotn_, Pavel Pecina and Jaroslav Pokorn_}{articles/289_Paper}

@@

\includepaper{SPARSE CODING BASED MUSIC GENRE CLASSIFICATION USING SPECTRO_TEMPORAL MODULATIONS}{Chih-Shan Lin, Kai-Chun Hsu and Tai-Shih Chi}{articles/046_Paper}

@@

\includepaper{Can Microblogs Predict Music Charts? An Analysis of the Relationship between #Nowplaying Tweets and Music Charts}{Eva Zangerle, Martin Pichl, Benedikt Hupfauf and Günther Specht}{articles/039_Paper}

>>>>

\includepaper{TIME-DELAYED MELODY SURFACES FOR RAGA RECOGNITION}{Sankalp Gulati, Joan Serrà, Kaustuv Kanti Ganguli, Sertan entürk and Xavier Serra}{articles/030_Paper}

@@

\includepaper{Further Steps towards a Standard Testbed for Optical Music Recognition}{Jan Haji, jr., Jií Novotn, Pavel Pecina and Jaroslav Pokorn}{articles/289_Paper}

@@

\includepaper{SPARSE CODING BASED MUSIC GENRE CLASSIFICATION USING SPECTRO-TEMPORAL MODULATIONS}{Chih-Shan Lin, Kai-Chun Hsu and Tai-Shih Chi}{articles/046_Paper}

@@

\includepaper{Can Microblogs Predict Music Charts? An Analysis of the Relationship between \#Nowplaying Tweets and Music Charts}{Eva Zangerle, Martin Pichl, Benedikt Hupfauf and Günther Specht}{articles/039_Paper}
